Austraits – a curated plant trait database for the Australian flora

### 2019-04-04 ms.Rmd
Updating table of traits with references

source("R/ms.R")

definitions <- austraits$definitions
```

@@

@@

data_geo <- 
  left_join(by=c("dataset_id", "site_name"),
      select(austraits$traits, -original_name), sites) %>%
  left_join(by="species_name",
      select(austraits$taxonomy, species_name, family))

n_records <- 
  data_geo %>% 
  group_by(trait_name) %>%
  summarise(
            Description = "",
            Type= "",
            `Records (all)` = n(),
            `Records (geo.)` = sum(!is.na(`longitude (deg)`) & !is.na(`latitude (deg)`)),
            Studies = n_distinct(dataset_id),
            Species = n_distinct(species_name),
            Families = n_distinct(family)
            )

n_records$Type <- sapply(austraits$definitions$traits$elements, "[[","type")[n_records$trait_name]
n_records$Description <- sapply(austraits$definitions$traits$elements, "[[","description")[n_records$trait_name]

n_records %>%
  arrange(desc(`Records (all)`)) %>% 
  slice(1:40) %>%
  kable()

@@

```{r, results='asis'}
c(austraits$methods$source_primary_citation %>% unique(),
austraits$methods$source_secondary_citation %>% unique()) %>% paste(collapse = "\n\n") %>% writeLines()
```

>>>>

source("R/ms.R")
```

@@

```{r austraits}

definitions <- austraits$definitions

sources_all <- 
  bind_rows(
    austraits$methods %>% select(dataset_id, citation = source_primary_citation) %>% distinct() %>% mutate(type="primary"),
    austraits$methods %>% select(dataset_id, citation = source_secondary_citation) %>% distinct() %>% mutate(type="secondary")
  ) %>% 
  na.omit() %>% 
  arrange(dataset_id)

sources_unique <- tibble(citation=unique(sources_all$citation)) %>% mutate(source_number=1:n())

sources_all <- sources_all %>% left_join(sources_unique, by = "citation")

refs <- sources_all %>% group_by(dataset_id) %>% 
  summarise(refs = paste(sort(source_number), collapse = ", "))

@@

trait_categories <- read_csv("data/trait_categories.csv")

data_geo <- 
  left_join(by=c("dataset_id", "site_name"),
      select(austraits$traits, -original_name), sites) %>%
  left_join(by="species_name",
      select(austraits$taxonomy, species_name, family)) %>% 
  left_join(refs, by=c("dataset_id"))

n_records <- 
  data_geo %>% 
  group_by(trait_name) %>%
  summarise(
            Description = "",
            Type= "",
            `Records (all)` = n(),
            `Records (geo.)` = sum(!is.na(`longitude (deg)`) & !is.na(`latitude (deg)`)),
            Studies = n_distinct(dataset_id),
            Species = n_distinct(species_name),
            Families = n_distinct(family),
            `Data Citations` = unique(refs) %>% paste(collapse = ", ")
            ) %>% 
  left_join(trait_categories, by=c("trait_name")) %>% 
  select(Tissue = tissue, Category = category, Trait = trait_name, everything()) %>% 
  arrange(Tissue, Category, Trait)

n_records$Type <- sapply(austraits$definitions$traits$elements, "[[","type")[n_records$Trait]
n_records$Description <- sapply(austraits$definitions$traits$elements, "[[","description")[n_records$Trait]

n_records %>%
  kable()
```

@@

```{r, results='asis'}
sprintf("%s. %s", sources_unique$source_number, sources_unique$citation) %>% paste(collapse = "\n\n") %>% writeLines()
```
